### 2022-11-14 NSF2022/Description/specificaim1v2.tex

The first step is to obtain some solid well-posedness results for
\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an autonomous
ordinary differential equation for the body transformations $F_i$ with
the rate of change defined by a system of PDEs. Regarding the PDE system,
in the linear case and for fixed $t$, there is a
unique solution ($\phi, \uu$) under appropriate assumptions for the
boundaries and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These
define instantaneous rigid body velocities and rotations,
leading to 
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection the closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and a smooth
  phase field boundary condition. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we
must establish that the system has a local-in-time solution. This
involves domain perturbations and estimates for the solutions of second
order elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example. For global-in-time solutions, we can 
use lubrication forces~\cite{cawthorn_balmforth_2010, leal_2007}.
Here, the lubrication force required to bring granules into contact
blows up with distance, whereas the attraction \eqref{eqn:stressbalance}
is finite, guaranteeing positivity in the distance between granules.
Finally, we can study the granule-flow behavior in the zero-decay length
limit. This limit should recover the hydrodynamics of a (noninteracting)
rigid-body suspension.

@@

Finally, to consider three-dimensionsional effects, we will generalize
Problem 2 to \emph{numerically} study the energies of amphiphilic
granules confined to surfaces. Recent works on nematics on a surface have
studied the interplay between surface geometry and a director
field~\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
Nitschke2020LiquidCO}. Researchers have formulated finite element
methods~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
Segatti2014AnalysisOA}. In biophysics, researchers
have derived the generalized Helfrich energy for lipid bilayers that
involves coupling effects between lipid tilt to director
splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
  Terzi2017NovelTC, Pinigin2020NewCT}. It contains~\eqref{eq:Canham-Helfrich}
as a special case.
\begin{quotation}
  \noindent
  \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
  amphilic granules. Numerically investigate the limiting energy for
  large-$N_b$ suspensions.
\end{quotation}
We will study Problem 3 by simulating large granule-number membranes.
If, after thoroughly sampling shapes and boundary conditions,
it turns out that the granule energies are not described by
a nematic or  Helfrich-type energy, then we will change
hypotheses and look for alternative sharp interface elastic energies.
PI Ryham is well-qualified to perform this investigation.
In the much noticed Biophysical Journal and Nature
papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy
paths for \emph{membrane fusion} using a surface-director model based on
the general Helfrich energy. The energy barriers 
proved consistent with later results from molecular dynamic
simulation and experiment~\cite{SmRiMu19, 2017PNAS..114.1238F}.

>>>>

The first step is to obtain some solid well-posedness results for
\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an autonomous
ordinary differential equation for the body transformations $F_i$ with
the rate of change defined by a system of PDEs. Regarding the PDE system,
in the linear case and for fixed $t$, there is a
unique solution ($\phi, \uu$) under appropriate assumptions for the
boundaries and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These
define instantaneous rigid body velocities and rotations,
leading to 
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection of closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and a smooth
  phase field boundary conditions. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we
must establish that the system has a local-in-time solution. This
involves domain perturbations and estimates for the solutions of second
order elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example. For global-in-time solutions, we can 
use lubrication forces~\cite{cawthorn_balmforth_2010, leal_2007}.
Here, the lubrication force required to bring granules into contact
blows up with distance, 
and we must analyze whether the attraction \eqref{eqn:stressbalance}
stays finite in order to  
guarantee positivity in the distance between granules.
Finally, we can study the granule-flow behavior in the zero-decay length
limit. This limit should recover the hydrodynamics of a (noninteracting)
rigid-body suspension.

@@

Finally, to consider three-dimensionsional effects, we will generalize
Problem 2 to \emph{numerically} study the energies of amphiphilic
granules confined to surfaces. Recent works on nematics on a surface have
studied the interplay between surface geometry and a director
field~\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
Nitschke2020LiquidCO}. Researchers have formulated finite element
methods~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
Segatti2014AnalysisOA}. In biophysics, researchers
have derived the generalized Helfrich energy for lipid bilayers that
involves coupling effects between lipid tilt to director
splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
  Terzi2017NovelTC, Pinigin2020NewCT}. It contains~\eqref{eq:Canham-Helfrich}
as a special case.
\begin{quotation}
  \noindent
  \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
  amphilic granules. Numerically investigate the limiting energy for
  large-$N_b$ suspensions.
\end{quotation}
We will study Problem 3 by simulating large granule-number membranes.
If, after thoroughly sampling shapes and boundary conditions,
it turns out that the granule energies are not described by
a nematic or  Helfrich-type energy, then we will change
hypotheses and look for alternative sharp interface elastic energies.
PI Ryham is well-qualified to lead this investigation.
In his much noticed Biophysical Journal and Nature
papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy
paths for \emph{membrane fusion} using a surface-director model based on
the general Helfrich energy. The energy barriers 
proved consistent with later results from molecular dynamic
simulation and experiment~\cite{SmRiMu19, 2017PNAS..114.1238F}.
